Differentiation with respect to weights for a `hyper3` object

### 2024-05-28 inst/grad_weight.Rmd
whitespace

```{r diffwrtw}
probs <- c(p1=0.15 , p2=0.45, p3=0.4)
diff <- (
 grad_weight_single(H, probs, c(p1=w), "p1") +
 grad_weight_single(H, probs, c(p1=w+D,p2=1+D), "p1") +
 grad_weight_single(H, probs, c(p2=w), "p2") +
 grad_weight_single(H, probs, c(p1=1+D,p2=w+D), "p2") +
 grad_weight_single(H, probs, c(p3=w), "p3")+
 grad_weight_single(H, probs, c(p3=w,p1=1),"p3")
 )

>>>>

```{r diffwrtw}
probs <- c(p1=0.15 , p2=0.45, p3=0.4)
diff <- (
 grad_weight_single(H, probs, c(p1=w)         , "p1") +
 grad_weight_single(H, probs, c(p1=w+D,p2=1+D), "p1") +
 grad_weight_single(H, probs, c(p2=w)         , "p2") +
 grad_weight_single(H, probs, c(p1=1+D,p2=w+D), "p2") +
 grad_weight_single(H, probs, c(p3=w)         , "p3") +
 grad_weight_single(H, probs, c(p3=w,p1=1)    , "p3")
 )
